ML-Runner: A Scalable Cloud System for Machine \& Distributed Learning

### 2018-05-11 Paper.tex
wo multicols

\title{ML-Runner: A Scalable Cloud System for Machine \& Distributed Learning \\ {\smaller \textbf{Project Report \YellowPaperVersionNumber}}}
\author{
    Barak Ben Noon (bb2762@columbia.edu) \\
    James Maxwell Stenger (jms2431@columbia.edu)
}
\begin{document}
\pagecolor{pagecolor}

@@

\maketitle
\setlength{\columnsep}{20pt}
\begin{multicols}{2}

@@

\end{multicols}
\subsubsection{Frontend}
We implemented a React front end which we deployed on an Nginx server on an AWS EC2 instance.
Our front end made use of a number of frameworks including:

@@

\begin{multicols}{2}
% -------------- FUTURE DIRECTIONS --------------
% -----------------------------------------------
\section{Future Directions} \label{ch:future}
In our application we used AWS Elastic Beanstalk to run the containerized experiments for each configuration, since this is what we were familiar with.
It may be preferable to use AWS Elastic Container Service instead, since we already package the code in docker containers, though due to time constraints we did not get a chance to investigate this option.

@@

\end{multicols}
\bibliographystyle{plainnat}
\bibliography{Biblio}

@@

\begin{Verbatim}[fontsize=\tiny, frame=single]
  a
\end{Verbatim}

In \ref{ch:future}, we outline how expensive on-chain storage is.

>>>>

\title{ML-Runner: A Scalable Cloud System for Machine \& Distributed Learning} %\\ {\smaller \textbf{Project Report \YellowPaperVersionNumber}}}
\author{
    Barak Ben Noon (bb2762@columbia.edu) \\
    James Maxwell Stenger (jms2431@columbia.edu)
}
\begin{document}
\pagecolor{pagecolor}

@@

\maketitle
\setlength{\columnsep}{20pt}
%\begin{multicols}{2}

@@

%\end{multicols}
\subsubsection{Frontend}
We implemented a React front end which we deployed on an Nginx server on an AWS EC2 instance.
Our front end made use of a number of frameworks including:

@@

%\begin{multicols}{2}
% -------------- FUTURE DIRECTIONS --------------
% -----------------------------------------------
\section{Future Directions} \label{ch:future}
In our application we used AWS Elastic Beanstalk to run the containerized experiments for each configuration, since this is what we were familiar with.
It may be preferable to use AWS Elastic Container Service instead, since we already package the code in docker containers, though due to time constraints we did not get a chance to investigate this option.

@@

%\end{multicols}
\bibliographystyle{plainnat}
\bibliography{Biblio}

@@

exports.handler = (event, context, callback) => {
  console.log( event)

  const MessageAttributes = {
    User: {
      DataType: "String",
      StringValue: event.user
    },
    ProjectName: {
      DataType: "String",
      StringValue: event.projectName
    },
    ProjectId: {
      DataType: "String",
      StringValue: event.projectId
    },
    S3key: {
      DataType: "String",
      StringValue: event.S3key
    },
  };

  var params = {
    DelaySeconds: 1,
    MessageAttributes,
    MessageBody: "Run",
    QueueUrl: "https://sqs.us-east-1.amazonaws.com/906385631751/ml-runner"
  };

  sqs.sendMessage(params, function(err, data) {
    if (err) {
      console.log("sendMessage with sqs:", err);
    } else {
      console.log("added new run to the queue")
    }
    return callback(null, true);
  });
};
\end{Verbatim}
